MP MetaAnalysis

### 2018-11-07 Paper_Analyses.Rmd
developmental focused manuscript, researcher choices analysis

@@

  Next to this core theoretically relevant investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations.

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.). The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes.

  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.  For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor. In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003). Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months. We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by whether the distractor used is familiar or unfamiliar. Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).  Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998). In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object. To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context. Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.

  Furthermore, when presenting infants with a familiar distractor image, some studies control the phonological overlap between the labels for the target and distractor. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. The influence of distractor overlap also depends on the position of the mispronunciation in the word, which can be at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word.  The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations. The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).

[KATIE] Christina had noted something to herself for this paragraph: Subset by language?

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Summary_Table). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Yet, studies testing infants from different language backgrounds on similar sets of stimuli find similar sensitivity to mispronunciations (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010). Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding. In our analysis, we examine the factors modulating the development of mispronunciation sensitivity, which are both of theoretical and practical importance. Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.

@@

dat_st$object_pair <- ifelse(dat_st$object_pair == "familiar_familiar", "Familiar", "Unfamiliar")

Sum_table <- dat_st %>%
      group_by(short_cite) %>% 
      summarise(Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))),
                Number_of_Features = paste(unique(n_feature), collapse=', '),
                Distractor_Familiarity = paste(unique(object_pair), collapse=', '),
                Distractor_Overlap = paste(unique(distractor_overlap), collapse=', '),
                Mispronunciation_Position = paste(unique(mispron_location), collapse=', '),
                Mispronunciation_type = paste(unique(type_feature), collapse=', '))

kable(Sum_table, col.names = c("Paper", "Age", "Vocabulary", "# Features", "Distractor", "Distractor name overlap", "MP Position", "MP Type"))

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
[KATIE] I'll think about how to implement that! Might end up having to adjust the table by hand, there is a lot of variation between studies.

@@

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics:   
1 Condition: Were words mispronounced or not;  
2 Mean age reported per group of infants, in days;  
3 Vocabulary size, measured by a standardized questionnaire or list;    
4 Size of mispronunciation, measured in features changed;  
5 Distractor familiarity: familiar or unfamiliar;  
6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
7 Position of mispronunciation: onset, medial, offset, or mixed;  
8 Type of mispronunciation: consonant, vowel, or both.

@@

## Figure 1

@@

## Figure 2

```{r PlotMPEffect, echo = FALSE}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        text = element_text(size = 40)) + 
  xlab("Age in months") + 
  ylab("Hedges' g")

p

@@

  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
       width = 700, height = 400, units = "px")

  p

@@

@@

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

## Moderator Analyses

[cHRISTINA] I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH HERE OR FLIP THE PARAGRAPH AROUND:
1. ARE DIFFERENT MODERATORS USED AT DIFFERENT AGES? 
TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
2. WHICH MODERATORS INFLUENCE MP SENSITIVITY
TEST SIMPLE MA WITH MODERATOR TESTS

OR 
"FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE DIFFICULT TASK "
ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES, AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY

[KATIE: I prefer this second option, first looking at the moderators in general and then looking at whether there is this systematic difference with age. The latter is exploratory, so I feel like this information should not preceed our planned analyses.]

### Number of features changed

```{r NFeatures_demographics}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

nfeature_info <- dat.f %>%
  group_by(n_feature) %>%
  summarize(n_exp_conditions =  n())

@@

To assess whether the number of features changed modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification in response to words that were pronounced correctly and mispronounced using 1-, 2-, and 3-feature changes. We did not include data for which the number of features changed in a mispronunciation was not specified or the number of features changed was not consistent (e.g., one mispronunciation included a 2-feature change whereas another only a 1-feature change). This analysis was therefore based on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` experimental conditions for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an equal impact on mispronunciation sensitivity, following the argument of graded sensitivity (White & Aslin, 2008; Mani & Plunkett 2011).

```{r NFeatures}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat.f, random = ~collapse | short_cite)

 sum_eff <- coef(summary(rma_NFeatures))[2,]

@@

To understand the relationship between number of features changed and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator. The moderator test was significant, `r mod_test(rma_NFeatures)`.  Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`. We plot this relationship in Figure 3. This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.

## Figure 3

```{r PlotFeatEffect, echo = FALSE}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "1-feature",
                         ifelse(dat_f$n_feature == 2, "2-feature",
                                ifelse(dat_f$n_feature == 3, "3-feature",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

dat_f <- subset(dat_f, feat_cat != "none")

dat_f$Features_changed <- factor(dat_f$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

p <- ggplot(dat_f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

p

  jpeg(filename = "figures/Figure_3_Number_of_Features.jpg", 
       width = 500, height = 300, units = "px")

  p

@@

  #[CHRISTINA] WHAT DO YOU THINK ABOUT VIOLIN PLOTS?

@@

```{r NFeatures_age}

dat.f  <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature)*age.C, data = dat.f, random = ~collapse | short_cite)

 sum_eff <- coef(summary(rma_NFeatures))[4,]

@@

```{r DistractorTypeAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

sum_eff <- coef(summary(rma_DistractorAge))[4,]

>>>>

# Create the function for mode.
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

@@

Taken together, the studies we have reviewed begin to paint a picture of the development of mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding. Meta-analyses can not only help us summarize the current state of research, but can also help us evaluate theories to drive future research and make hands-on recommendations for experiment planning.

@@

Sum_table <- dat_st %>%
      group_by(short_cite) %>% 
      summarise(Publication = unique(publication_status),
        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comprehension/Production",
                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comprehension", "Production"))))

kable(Sum_table, col.names = c("Paper", "Publication format", "Age", "Vocabulary"))

@@

[KATIE] THIS TABLE IS DEFINITELY NOT FINISHED!
[CHRISTINA suggestions: N features should be a range and exclude 0; we could abbreviate Comperehension/Production to Comp./Prod., etcetc]
[KATIE] I've reduced the table to be about age and vocabulary, in order to have it more focused for the aim of this paper.

@@

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics:

1 Condition: Were words mispronounced or not;  
2 Mean age reported per group of infants, in days;  
3 Vocabulary size, measured by a standardized questionnaire or list;

@@

## (Insert Figure 1 about here)

@@

## (Insert Figure 2 about here)

```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  ggtitle("a. Object Recognition")+
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

#p

dat.cm <- dat[,c("short_cite", "is_correct", "is_mp","condition", "g_calc", "weights_g", "mean_age_1", "n_1")]

dat.c <- subset(dat.cm, is_correct == 1)
dat.m <- subset(dat.cm, is_mp == 1)

dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "mean_age_1", "n_1"))

dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = n_1),show.legend=FALSE, alpha = .5) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Mispronunciation Sensitivity")

@@

lay <- rbind(c(1), c(2))
#lay <- rbind(c(1,2))

  jpeg(filename = "figures/Figure_2_AgeEffect.jpg", 
       width = 500, height = 700, units = "px")

ger.plot.age <- grid.arrange(p, p.diff,
                             layout_matrix = lay)

@@

grid.draw(ger.plot.age)

@@

Alternatively, it is possible that variation in the analysis approach lead to systematic differences in the size of mispronunciation sensitivity. Choices about the approach to data analysis have a higher possibility to be influenced by the shape of the data itself after collection, and are therefore susceptible to a higher rate of false-positives (Simmons, Nelson, & Simonsohn, 2011). Although we did not have specific predictions about these variables, such as size of time window analyzed or dependent variable calculated, we included these variables in our coding scheme for the meta-analysis dataset. As reported in the Methods section (and discussed in detail below), some of these variables varied widely across studies. In the following section, we include an exploratory analysis to investigate the possibility of systematic differences in the approach to analysis in general and across infant age.

[KATIE] I've changed the above paragraph to lead to exploratory analyses, not moderators. Since the fmailiar/unfamiliar analysis doesn't really work out except for if we kind of subset and torture the data, I think its more interesting to talk about how choices of analysis / researcher degrees of freedom may influence the data

## Exploratory Analyses

We identified several variables to assess the influence of data analysis choices. These variables fall into two types of categories: time-related and dependent variable related. In the following analyses, we discuss the theoretical motivation for these data analysis choices, the variation present in the current meta-analysis dataset, and the influence these choices have on mispronunciation sensitivity development.

### Time-related analyses

```{r time_choices_info}

# trial length

trial_length_info <- dat %>%
  group_by(trial_length) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

trial.l <- cor.test(dat$trial_length, dat$mean_age_1)
trial.length.plot <- ggplot(dat, aes(trial_length, age.C)) + geom_point() +geom_smooth(method = "lm")

# post-naming
post_name_info <- dat %>%
  group_by(post_nam_dur) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

post.l <- cor.test(dat$post_nam_dur, dat$mean_age_1)
post_nam_dur.plot <- ggplot(dat, aes(post_nam_dur, age.C)) + geom_point() +geom_smooth(method = "lm")

# difference post vs. trial length
dat$post_trial_match <- ifelse(dat$post_nam_dur == (dat$trial_length-dat$pre_nam_dur), "same", "different")
dat$post_trial_prop <- dat$post_nam_dur/(dat$trial_length-dat$pre_nam_dur)

post_trial_match_info <- dat %>%
  group_by(post_trial_match) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

post_trial_prop_info <- dat %>%
  group_by(post_trial_prop) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

post_match.l <- cor.test(dat$post_trial_prop, dat$mean_age_1)
post_match.plot <- ggplot(subset(dat, post_trial_prop != 1), aes(post_trial_prop, age.C)) + geom_point() +geom_smooth(method = "lm")

# offset
offset_info <- dat %>%
  group_by(offset) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

dob <- subset(dat, !is.na(offset) & offset < 1000)
dob$offset_bin <- ifelse(dob$offset <371 & dob$offset > 359, 367, dob$offset)

# offset
offset_bin_info <- dob %>%
  group_by(offset_bin) %>%
  summarize(n_exp_conditions =  n())
        #post_naming = paste(unique(post_nam_dur), collapse=', '))

offset.l <- cor.test(dat$offset, dat$mean_age_1)
offset.plot <- ggplot(dat, aes(offset, age.C)) + geom_point() +geom_smooth(method = "lm")

@@

When designing mispronunciation sensitivity studies, experimenters choose the length of time each trial is presented. This includes both the length of time before the target object is named (pre-naming phase) as well as after (post-naming phase) and is determined prior to data collection. Across papers, trial length varied from `r with(trial_length_info, min(trial_length))*1000` to `r with(trial_length_info, max(trial_length))*1000` ms, with a mode of `r with(dat, getmode(trial_length))*1000` ms. There was an inverse relationship between infant age and trial length, such that younger infants were given trials of a longer length, although this correlation was not significant (*r* = `r trial.l$estimate`, *p* `r psig(trial.l$p.value)`). Presumably, younger infants may be given longer trials because their word recognition abilities may be slower than older infants (Fernald et al., 1998).

Unlike the length of trial, the length of the post-naming phase analyzed can be chosen after the experimental data is collected. Interestingly, half of the experimental conditions were analyzed using the same length of post-naming phase as the infant heard in the actual experiment `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "same"])`, while the other half were analyzed using a shorter length of post-naming phase, excluding later portions of the post-naming phase `r with(post_trial_match_info, n_exp_conditions[post_trial_match == "different"])`. Across papers, the length of the post-naming phase analyzed varied from `r with(post_name_info, min(post_nam_dur))*1000` to `r with(post_name_info, max(post_nam_dur))*1000` ms, with a mode of `r with(dat, getmode(post_nam_dur))*1000` ms. Similar to trial length, there was an inverse relationship between infant age and length of post-naming phase analyzed, such that younger infants were analyzed using a longer length of post-naming phase, although here the relationship was significant (*r* = `r post.l$estimate`, *p* `r psig(post.l$p.value)`). Again, the choice to analyze a shorter post-naming time window is likely related to evidence that speed of processing is slower in younger infants (Fernald et al., 1998). Furthermore, the proportion of post-naming phase time window analyzed in comprison to the total post-naming phase presented to infants significantly decreased with increasing infant age (*r* = `r post_match.l$estimate`, *p* `r psig(post_match.l$p.value)`). Although trial length did not differ by infant age, the size of the post-naming phase time window analyzed did differ by infant age.

When analyzing eye-movements, it is important to consider the amount of time it takes for an eye movement to be initiated in response to a stimulus. Previous studies examining simple stimulus response latencies first determined that infants require at least 233 ms to initiate an eye-movement in response to a stimulus (Canfield & Haith, 1991). In mispronunciation sensitivity studies, however, this has often been extended to 367 ms (e.g. Swingley & Aslin, 2000, 2002, 2007). Across papers, the majority used a similar offset value (between 360 and 370 ms) for analysis (*n* = `r with(offset_bin_info, n_exp_conditions[offset_bin == "367"])`), but offset values ranged from `r with(offset_bin_info, min(offset_bin))` to `r with(offset_bin_info, max(offset_bin))` ms, and were not reported for `r with(offset_info, n_exp_conditions[is.na(offset)])` experimental conditions. We note that Swingley (2009) also included offset values of 1133 ms to analyze responses to coda mispronunciations. There was an inverse relationship between infant age and size of offset, such that younger infants were given longer offsets, although this correlation was not significant (*r* = `r offset.l$estimate`, *p* `r psig(offset.l$p.value)`). This lack of a relationship is perhaps driven by the field's consensus that an offset of about 367 ms is appropriate for analyzing word recognition with PTL measures, including studies that evaluate mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time window (infant age) or offset time (previous studies), these choices may occur after data collection and are therefore susceptible to a higher rate of false-positives. Considering that differences in these choice were systematically different across infant ages, at least for the post-naming time window, we next explored whether the size of the analyzed post-naming phase time window or the offset time influenced sensitivity to mispronunciations.

### Length of post time

```{r time_post}

rma_post_dur <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur), data = db_ET_MP, random = ~collapse | short_cite)

 rma_post_dur_eff <- coef(summary(rma_post_dur))[2,]

 rma_post_dur_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*condition, data = dat, random = ~collapse | short_cite)

  rma_post_dur_MS_eff <- coef(summary(rma_post_dur_MS))[4,]

  # age

 rma_post_dur_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C, data = db_ET_MP, random = ~collapse | short_cite)

   rma_post_dur_AGE_eff <- coef(summary(rma_post_dur_MS))[4,]

  rma_post_dur_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(post_nam_dur)*age.C*condition, data = dat, random = ~collapse | short_cite)

    rma_post_dur_AGE_MS_eff <- coef(summary(rma_post_dur_MS))[8,]

@@

We first assessed whether size of post-naming phase analyzed had an impact on the size of mispronunciation sensitivity. First, we calculated the meta-analytic effect for object identification in response to mispronounced target words/images, including post-naming phase size as a moderator. The moderator test was not significant `r mod_test(rma_post_dur)` and the estimate for post-naming phase size was relatively small, $\beta$`r full_estimate(rma_post_dur_eff)`. This suggests that upon hearing a mispronunciation, infants' looks to the target image were similar regardless of the size of the post-naming phase analyzed. We next assessed whether post-naming phase size was related to mispronunciation sensitivity. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as an additional moderator. The moderator test was significant, `r mod_test(rma_post_dur_MS)`. The estimate for the interaction between post-naming phase size and condition was small but significant $\beta$`r full_estimate(rma_post_dur_MS_eff)`. This relationship is plotted in Figure 3a. The results suggest that although the size of the post-naming phase analyzed did not impact infants' likelihood to fixate the target upon hearing the mispronunciation, it did significantly impact mispronunciation sensitivity. Specifically, the difference between target fixations for correctly pronounced and mispronounced items (mispronunciation sensitivity) was significantly greater when the post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the post-naming phase analyzed and infant age, such that younger ages had a longer post-naming phase time window of analysis, we next examined whether the size of post-naming phase analyzed modulated the development of mispronunciation sensitivity. For object recognition in response to a mispronunciation, including age as a moderator resulted in a moderator test that was not significant `r mod_test(rma_post_dur_AGE)`, and a small estimate for the interaction between age and size of post-naming phase ($\beta$`r full_estimate(rma_post_dur_AGE_eff)`. This suggests that upon hearing a mispronunciation, infant measured looks to the target image were similar, regardless of infant age or size of the post-naming phase analyzed. We next assessed whether the relationship between size of the post-naming phase analyzed and mispronunciation sensitivity was modulated by age. We merged the two datasets and included condition (correct pronunciation, mispronunciation) as well as age as additional moderators. The moderator test was significant `r mod_test(rma_post_dur_AGE_MS)`. The estimate for the  three-way-interaction between condition, size of post-naming phase, and age was small, but significant ($\beta$ = `r full_estimate(rma_post_dur_AGE_MS_eff)`. This relationship is plotted in Figure 3b. Smaller post-naming phase size lead to greater increases in mispronunciation sensitivity with development. For example, experimental conditions analyzed with a post-naming phase of 2000 ms or less, mispronunciation sensitivity increases with infant age, whereas a post-naming phase of greater than 2000 ms leads to either no impact of age on mispronunciation sensitivity or a negative relationship between age and mispronunciation sensitivity.

## (Insert Figure 3 about here)

```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11}

dat$condition_label <- ifelse(dat$condition==1, "Correct", "Mispronunciation")

dat$post_size <- ifelse(dat$post_nam_dur <= 2, "2000 ms or less",
                       ifelse(dat$post_nam_dur > 2 & dat$post_nam_dur <= 3, "2001-3000 ms", "3001 ms or greater"))

dat$post_size <- factor(dat$post_size, levels = c("2000 ms or less", "2001-3000 ms", "3001 ms or greater"))

dat.cm <- dat[,c("short_cite", "is_correct", "is_mp", "post_size", "condition", "g_calc", "weights_g", "mean_age_1", "n_1")]

dat.c <- subset(dat.cm, is_correct == 1)
dat.m <- subset(dat.cm, is_mp == 1)

dat.cm <- merge(dat.c, dat.m, by = c("short_cite", "post_size", "mean_age_1", "n_1"))

dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y

p.MS <- ggplot(dat.cm, aes(post_size, Misp_sensitivity, fill = post_size)) + 
  #facet_grid(.~post_size)+
    geom_violin() + 
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(caption="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
    #facet_grid(.~post_size)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(caption="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

lay <- rbind(c(1), c(2))
#lay <- rbind(c(1,2))

  jpeg(filename = "figures/Figure_3_Post_name_size.jpg", 
       width = 600, height = 600, units = "px")

ger.plot.age <- grid.arrange(p.MS, p.AGE,
                             layout_matrix = lay)

@@

grid.draw(ger.plot.age)

@@

### Length of offset time

```{r time_offset}

rma_offset <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset), data = db_ET_MP, random = ~collapse | short_cite)

rma_offset_eff <- coef(summary(rma_offset))[2,]

 rma_offset_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*condition, data = dat, random = ~collapse | short_cite)

  rma_offset_MS_eff <- coef(summary(rma_offset_MS))[4,]

  # age

 rma_offset_AGE <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C, data = db_ET_MP, random = ~collapse | short_cite)

   rma_offset_AGE_eff <- coef(summary(rma_offset_AGE))[4,]

  rma_offset_AGE_MS <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(offset)*age.C*condition, data = dat, random = ~collapse | short_cite)

    rma_offset_AGE_MS_eff <- coef(summary(rma_offset_AGE_MS))[8,]

@@

## Controlling for researcher choice

```{r reanalysis_misp_sens_dv_label}

dat$dv_label <- ifelse(dat$within_measure=="post", "Post",
                       ifelse(dat$within_measure == "pre_post", "Post vs. Pre",
                              "Difference Score"))

dat$dv_label <- factor(dat$dv_label, levels = c("Post", "Post vs. Pre", "Difference Score"))
